Analysis of nested multilevel Monte Carlo \\ using approximate Normal random variables\footnote{{This material is on arXiv and contained in O.\ Sheridan-Methven's PhD thesis.}}

### 2021-02-16 paper.tex
Put paper in form for SIAM UQ.
Added footnote of authorship.

\documentclass[11pt]{article}

\usepackage{amsmath,amsthm,amssymb,amscd}

\usepackage{float}
\usepackage[caption = false]{subfig}
\usepackage[final]{graphicx}

\usepackage{xcolor}
%\usepackage{natbib}
\usepackage{todonotes}
\usepackage[colorlinks,citecolor = red,urlcolor=blue]{hyperref}

@@

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{assumption}[theorem]{Assumption}
%\newenvironment{proof}{
% \bgroup\noindent\small{\bf Proof\ }}{
% \nolinebreak\hbox{\ $\Box$}\\
% \egroup}

@@

\title{Analysis of nested multilevel Monte Carlo \\ using approximate Normal random variables}

\author{
Mike Giles
\thanks{\href{mailto:mike.giles@maths.ox.ac.uk}%
{\texttt{mike.giles@maths.ox.ac.uk}}}
\and 
Oliver Sheridan-Methven
\thanks{\href{mailto:oliver.sheridan-methven@hotmail.co.uk}%
{\texttt{oliver.sheridan-methven@hotmail.co.uk}}}
}

@@

@@

\bibliographystyle{unsrt}
\bibliography{mlmc,mc}

>>>>

\documentclass[review]{siamart190516}

\usepackage{amsmath,amssymb,amscd}

\usepackage{float}
\usepackage[caption = false]{subfig}
\usepackage[]{graphicx}

\usepackage{xcolor}
%\usepackage{natbib}
\usepackage{todonotes}
%\usepackage[colorlinks,citecolor = red,urlcolor=blue]{hyperref}

@@

%\newtheorem{theorem}{Theorem}[section]
%\newtheorem{lemma}[theorem]{Lemma}
%\newtheorem{proposition}[theorem]{Proposition}
%\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{assumption}[theorem]{Assumption}
%\newenvironment{proof}{
% \bgroup\noindent\small{\bf Proof\ }}{
% \nolinebreak\hbox{\ $\Box$}\\
% \egroup}

@@

\title{Analysis of nested multilevel Monte Carlo \\ using approximate Normal random variables\footnote{{This material is on arXiv and contained in O.\ Sheridan-Methven's PhD thesis.}}}

\author{
Mike Giles%
\thanks{\href{mailto:mike.giles@maths.ox.ac.uk}%
{\texttt{mike.giles@maths.ox.ac.uk}}}
\and 
Oliver Sheridan-Methven%
\thanks{\href{mailto:oliver.sheridan-methven@hotmail.co.uk}%
{\texttt{oliver.sheridan-methven@hotmail.co.uk}}}
}

@@

\begin{keywords}
approximations, random variables, the Normal distribution, multilevel Monte Carlo, the Euler-Maruyama scheme, the Milstein scheme, and high performance computing.
\end{keywords}

% cf. https://mathscinet.ams.org/mathscinet/msc/msc2020.html
\begin{AMS}
65C10, 65C05, 65Y20, 60H35, and 65C30.
\end{AMS}

@@

\bibliographystyle{siamplain}
\bibliography{mlmc,mc}
